\bf Interactive Visualization of Hierarchically Structured Data

### 2017-07-11 treelapse.tex
add description of scalability
(also, changed line lengths for a few sections)

We have implemented our visualizations in D3, but encapsulated in an R
package, called treelapse, to facilitate rapid turnover from data
preparation and modeling to interactive exploration, and vice versa. Our
code is open-source, and available at
\url{https://github.com/krisrs1128/treelapse}\footnote{Link removed in blinded manuscript,
but available to editor.}. We hope this package encourages data analysts
to work at the border between data modeling and visualization, and more
generally empowers a wider audience to apply less widely known, but
powerful, visualization ideas.

@@

@@

{\centering \includegraphics[width=350px]{figure/antibiotic_firmicutes}

>>>>

We have implemented our visualizations in D3, but encapsulated in an R package,
called treelapse, to facilitate rapid turnover from data preparation and
modeling to interactive exploration, and vice versa. Our code is open-source,
and available at \url{https://github.com/krisrs1128/treelapse}. We hope this
package encourages data analysts to work at the border between data modeling and
visualization, and more generally empowers a wider audience to apply less widely
known, but powerful, visualization ideas.

@@

To be practically useful, the resulting visualizations must respond fluidly to
user interaction. As the data increase in scale, this fluidity can deteriorate
for two reasons. First, rendering many SVG elements in a framework like D3 is
costly\citep{johnson2008scalability}. While it is possible to use alternatives
-- HTML5's Canvas, for example -- it is often more challenging to implement
complex interactive behavior through them. Second, some of the dynamic queries
require a search over a many elements. These limitations are most pronounced in
the timebox tree display, which must search through all timepoints among all
time series whenever the brush is moved. The first, but not the second, concern
applies to treeboxes, while neither applies to DOI trees. Nonetheless, we feel
comfortable recommending timebox trees for data on the order of 500 tree tips
and 50 timepoints We note the sizes of the data sets in each case study below,
which each render fluidly, with the possible exception of the California housing
data, where there is a noticeable lag in the timebox tree and treebox displays.

@@

\begin{figure}
{\centering \includegraphics[width=350px]{figure/antibiotic_firmicutes}
